Missing the Point: Detecting Non-Convergence in Multiple Imputation Procedures

### 2020-03-26 3.Thesis/1.SimulationStudy/Writeup/manuscript.tex
Ran sim to show Gerko new plots (mean, var, est, pred).

  pdftitle={Missing the Point: Convergence of Multiple Imputation by Chained Equations Algorithms},

@@

\title{Missing the Point: Convergence of Multiple Imputation by Chained
Equations Algorithms}
\author{Hanne I. Oberman}
\date{16-3-2020}

@@

>>>>

  pdftitle={Missing the Point: Detecting Non-Convergence in Multiple Imputation Procedures},

@@

\title{Missing the Point: Detecting Non-Convergence in Multiple Imputation
Procedures}
\author{Hanne I. Oberman}
\date{16-3-2020}

@@

What to evaluate?

\begin{itemize}
\item
  bias in regression coefficients
\item
  bias in \(R^2\) (= coefficient of determination)
\item
\end{itemize}
